% LaTeX resume using res.cls
\documentclass[line,margin]{res}
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)

\setlength{\oddsidemargin}{-.2in}
\setlength{\textwidth}{5.2in}

\begin{document}
    \name{\LARGE Adam Black}
    \address{ablack@fastmail.net}
    \address{0401 868 343}

    \begin{resume}
        \section{Profile}
        Highly motivated software engineer with a passion for developing code and solving problems.

        6 years of professional experience including 4 years in software development and 2 years in
        QA. Exposure to a wide range of programming languages and both object oriented and functional
        paradigms. Highly competent using Microsoft Windows and Linux. Tertiary qualified in computer
        science and telecommunications.

        \section{Skills}
        \begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-2pt}
            \item{\textbf{Languages}: Python, VB .NET, C++, JavaScript}
            \item{\textbf{Frameworks}: MVC 5, Entity Framework 6, jQuery}
            \item{\textbf{DBMS}: MS SQL Server, Firebird, SQLite}
            \item{\textbf{Editors}: Vim, Visual Studio, Eclipse}
            \item{\textbf{VCS}: GIT, Subversion}
            \item{\textbf{Server Applications}: Apache, BIND, Samba, Buildbot, Asterisk, IIS}
            \item{\textbf{OS}: Linux, Unix, OS X, Windows}
        \end{list}

        \section{Experience}
        \textbf{IRESS}, Melbourne, VIC \hfill Aug 2012 - present \\
        \textit{Research Software Developer} for one of the leading suppliers of innovative technology
        solutions for the financial markets, wealth management, and mortgage sectors.

        \textit{Responsibilities}:
        \begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-2pt}
            \item{Design and implement features in XPLAN, a financial planning application written in Python.}
            \item{Fix bugs and refactor code.}
            \item{Primary developer and maintainer of VB .NET web application used to input superannuation
                research data.}
            \item{Update business logic in Firebird stored procedures.}
            \item{Provide technical support to research analysts.}
            \item{Configure automated builds and deployments in TeamCity.}
        \end{list}

        \textit{Deliverables}:
        \begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-2pt}
            \item{Introduced a flexible new system for storing provider fees and managed the
                associated data migration issues.}
            \item{Migrated legacy Visual Basic 6 desktop application to Visual Basic .NET.}
            \item{Incorporated Entity Framework 6 into product to improve data access code.}
            \item{Seamlessly integrated MVC5 into webapp to allow pages to be
                progressively updated from WebForms to MVC.}
        \end{list}

        \textbf{Daintree Networks}, Scoresby, VIC \hfill Feb 2010 to July 2012 \\
        \textit{QA Automation Engineer} for the market leader in smart building control.

        \textit{Responsibilities}:
        \begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-2pt}
            \item{Lead the design and development of a Python-based test automation system.}
            \item{Test wireless embedded (ZigBee) platform.}
            \item{Debug and analyse transactions in a ZigBee network.}
            \item{Linux network and services administration: BIND, dhcp3-server, Apache, Samba, Buildbot}
            \item{Document test plans and test cases.}
            \item{Work in an agile environment.}
        \end{list}

        \textit{Deliverables}:
        \begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-2pt}
            \item{Increased automated test coverage by implementing the required infrastructure and
                test cases.}
            \item{Developed analysis tools used by the marketing team to scope hardware
                requirements for customer deployments.}
            \item{Developed a library for simulating various Modbus power meters using modbus-tk.}
            \item{Created a custom Linux installer to streamline the deployment of core product.}
        \end{list}

        \textbf{Centre for Advanced Internet Architectures},\hfill Feb 2007 - Jan 2008 \\
        Swinburne University of Technology Hawthorn, VIC \\
        \textit{Research Assistant (Industry Based Learning)}\\

        \begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-2pt}
            \item{Analysed the network traffic characteristics of various multi-player game engines using
            py-libpcap.}
            \item{Created a Wireshark plugin in C for dissecting VTun packets.}
            \item{Measured the power fluctuations in consumer ADSL modems as a function of network traffic.}
            \item{Used a Dummynet bridge to introduce latency and jitter between hosts.}
        \end{list}

        \section{Education}
        \textbf{Swinburne University of Technology} \hfill 2010\\
        \textit{B.Eng - Telecommunications and Internet Technology / B.Sci - Computer Science and
        Software Engineering}

        \textit{Awards}:
        \begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-2pt}
            \item{First class honors in Bachelor of Engineering.}
            \item{Faculty of ICT award for the most outstanding final year student in 2010 in the B.Eng -
                Telecommunications and Internet Technology / B.Sci - Computer Science and Software
                Engineering).}
            \item{Ericsson Award for the highest achieving student in Broadband Multimedia Networks.}
            \item{Australia Arrow Award for the highest achieving student in Software Engineering Project B.}
            \item{Highest achieving student in Communication Information Theory.}
        \end{list}

        \section{Interests}
        \begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-2pt}
            \item{Squash}
            \item{Weight training and fitness}
            \item{Woodworking}
            \item{Cycling}
        \end{list}

        \section{References}
        Available upon request.
    \end{resume}
\end{document}

